CMPEN/EE 454 Project 2 Report

### 2015-12-12 p2/report/project_report.tex
maybe done with matching?

\newpage
\pagenumbering{arabic}
\setcounter{page}{1}
\section{Integral Algorithms}
\subsection{Harris Corner Detection}
\subsubsection{Synopsis}
Harris corner detection is an algorithm which detect corners in images that can be used to create point correspondences between time series images.  A ``corner'' can loosely be defined as a feature in the image located at coordinates $(x_0,y_0)$ such that $\frac{\partial f}{\partial x}(x_0,y_0)$ and $\frac{\partial f}{\partial y}(x_0,y_0)$ yield relatively large values.
\subsubsection{Implementation}
Below the implementation of the Harris corner detection algorithm in C-like pseudocode.
\begin{lstlisting}

@@

	// Finally, any pixel with a value of 1 in the binary image
	// is considered a corner point coordinate.
	for (px : b_img) {
		p_arr += px;
	}

	return p_arr;
}

@@

assignment_set compute_cost(bounding_box a,b) {

	// Compute the costs of corresponding each corner
	// point in bounding box a against every corner
	// point in bounding box b.
	for (corner c_a : a) {
	for (corner c_b : b) {
		// Get the image patches around each corner point.
		patch_a = get_patch(c_a);
		patch_b = get_patch(c_b);

		// Use SSD as cost function.
		cost_matrix[i, j] =
			sum_squared_difference(patch_a, patch_b);
	} }

@@

>>>>

\newpage
\pagenumbering{arabic}
\setcounter{page}{1}
\section{Integral Algorithms}
\subsection{Harris Corner Detection}
\subsubsection{Synopsis}
Harris corner detection is an algorithm which detect corners in images that can be used to create point correspondences between time series images.  A ``corner'' can loosely be defined as a feature in the image located at coordinates $(x_0,y_0)$ such that $\frac{\partial I}{\partial x}(x_0,y_0)$ and $\frac{\partial I}{\partial y}(x_0,y_0)$ yield relatively large values.
\subsubsection{Implementation}
Below the implementation of the Harris corner detection algorithm in C-like pseudocode.
\begin{lstlisting}

@@

	// Finally, any pixel with a value of 1 in the binary image
	// is considered a corner point coordinate.
	// 
	// The notation for(x:y) is used to mean "for each element x
	// in the set y."
	for (px : b_img) {
		p_array.add(px);
	}

	return p_array;
}

@@

assignment_set compute_bb_set(bounding_box a,b) {

	// Compute the costs of corresponding each corner
	// point in bounding box a against every corner
	// point in bounding box b.
	for (corner_a : a) {
	for (corner_b : b) {
		// Get the image patches around each corner point.
		patch_a = get_patch(corner_a);
		patch_b = get_patch(corner_b);

		// Use SSD as cost function.
		cost_matrix[corner_a, corner_b] =
			sum_squared_difference(patch_a, patch_b);
	} }

@@

\end{lstlisting}
\end{minipage}
\\~\\
For the bounding boxes pictured below, here is an example assignment set:
\[
\left \{
\begin{tabular}{c}
$(G \iff J,\quad \text{SSD}_{GJ})$ \\
$(F \iff K,\quad \text{SSD}_{FK})$ \\
$(I \iff M,\quad \text{SSD}_{IM})$ \\
$(E \iff \emptyset,\quad \infty)$ \\
$(H \iff \emptyset,\quad \infty)$
\end{tabular}
\right \}
\]
The overall cost of assigning Bounding Box 1 to Bounding Box 2 is then the sum of the finite costs in the optimal assignment set; i.e. $\text{SSD}_{GJ} + \text{SSD}_{FK} + \text{SSD}_{IM}$.
\begin{center}
\fbox{\includegraphics[width=0.65\textwidth]{box_corners}}
\end{center}
~\\
A similar method is used to find an optimal bounding box correspondence between two images:
\\
\begin{minipage}{\textwidth}
\begin{lstlisting}

assignment_set compute_img_set(image a,b) {

	// Compute the costs of corresponding each bounding box
	// in image a against every bounding box in image b.
	for (bounding_box_a : a) {
	for (bounding_box_b : b) {

		bb_set =
		compute_bb_set(bounding_box_a, bounding_box_b);

		// Sum the costs for the valid assignments
		total_cost = 0;
		for (assignment : bb_set) 
			if (assignment.cost < inf)
				total_cost += assignment.cost;

		cost_matrix[bounding_box_a, bounding_box_b] =
			total_cost;

	} }

	return assignmentoptimal(cost_matrix);
}
